Postural changes mediate children's visual access to social information

### 2018-01-18 writeup-cogsci-jan14/cogsci2018_faceOnly.tex

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
 & Algorithm & Sample\ Type & P & R & F \\ 
  \hline
1 & MTCNN & High\ density & 0.841 & 1.000 & 0.914 \\ 
  2 & MTCNN & Random & 0.947 & 0.750 & 0.837 \\ 
  3 & OpenPose & High\ density & 0.995 & 0.863 & 0.924 \\ 
  4 & OpenPose & Random & 0.710 & 0.917 & 0.800 \\ 
  5 & ViolaJones & High\ Density & 0.991 & 0.495 & 0.660 \\ 
  6 & ViolaJones & Random & 0.389 & 0.292 & 0.333 \\ 
   \hline
\end{tabular}
\caption{Detector performance.} 
\end{table}

@@

To formalize these observations, we fit a generalized logistic
mixed-effect model to all with the presence/absence of a face on every
frame as the dependent variable, and participant's age, orientation, and
posture as predictors. Interactions between predictors were not included
as this maximal model failed to converge. A summary of the coefficients
of this model can be found in Table 3 for the MTCNN detections, though
we found the same pattern of results for the OpenPose detections. While
age remained a significant predictor even when accounting for the
effects of infants' posture and orientation, it accounted for the least
amount of variance. Overall, these results suggest that, instead,
infants' access to faces is heavily infleunced by their own posture and
theirorientation towards their caregiver.

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.847 & 0.064 & -75.303 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.075 & 2.273 & 0.023 \\ 
  postureprone & -0.513 & 0.042 & -12.326 & 0.000 \\ 
  posturesit & 0.648 & 0.039 & 16.422 & 0.000 \\ 
  posturestand & 1.005 & 0.041 & 24.721 & 0.000 \\ 
  orientationclose & 1.549 & 0.022 & 71.940 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 100.357 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model prediting the presence/absence of a face (MTCNN-Faces) across the entire dataset.} 
\end{table}

@@

\caption[Proportion face detections around a naming instance ('Look, a Zem']{Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utternace) as a function of infants's posture. Each point represents a naming instance for each child in the dataset.}\label{fig:detByNaming}
\end{figure}
\end{CodeChunk}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
 & Algorithm & Sample\ Type & P & R & F \\ 
  \hline
1 & MTCNN & High\ density & 0.841 & 1.000 & 0.914 \\ 
  2 & MTCNN & Random & 0.947 & 0.750 & 0.837 \\ 
  3 & OpenPose & High\ density & 0.995 & 0.863 & 0.924 \\ 
  4 & OpenPose & Random & 0.710 & 0.917 & 0.800 \\ 
  5 & ViolaJones & High\ Density & 0.991 & 0.495 & 0.660 \\ 
  6 & ViolaJones & Random & 0.389 & 0.292 & 0.333 \\ 
   \hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of faces detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively.} 
\end{table}

@@

To formalize these observations, we fit a generalized logistic
mixed-effect model to all with the presence/absence of a face on every
frame as the dependent variable, and participant's age, orientation, and
posture as predictors. Interactions between predictors were not included
as this maximal model failed to converge. A summary of the coefficients
of this model can be found in Table 3 for the MTCNN detections, though
we found the same pattern of results for the OpenPose detections. While
age remained a significant predictor even when accounting for the
effects of infants' posture and orientation, it accounted for the least
amount of variance. Overall, these results suggest that, instead,
infants' access to faces is heavily infleunced by their own posture and
their orientation towards their caregiver.

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.847 & 0.064 & -75.303 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.075 & 2.273 & 0.023 \\ 
  postureprone & -0.513 & 0.042 & -12.326 & 0.000 \\ 
  posturesit & 0.648 & 0.039 & 16.422 & 0.000 \\ 
  posturestand & 1.005 & 0.041 & 24.721 & 0.000 \\ 
  orientationclose & 1.549 & 0.022 & 71.940 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 100.357 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model predicting the presence/absence of a face (MTCNN-Faces) across the entire dataset.} 
\end{table}

@@

\caption[Proportion face detections around a naming instance ('Look, a Zem']{Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture. Each point represents a naming instance for each child in the dataset.}\label{fig:detByNaming}
\end{figure}
\end{CodeChunk}
